Winter weather on exam days and matriculation for a prestigious university in Japan

### 2021-04-03 Writeups/paper.tex
Revision done

This study analyzes the effect of winter weathers on exam outcomes in Japan.
Most public universities in Japan require high school seniors and graduates to take a centralized test, called National Center Test for University Admission (Center Test henceforth), for admission.
Students take the exam on the same dates in mid-January in their prefectures.
This creates a variation in weathers to which they are exposed to on the exam dates.
I use the weather on the dates of Center Test and investigate its effect on the matriculation for the University of Tokyo (UTokyo henceforth).
The advantage of using the matriculation share for UTokyo as an outcome is that it is the most prestigious university in Japan.
This allows me to attribute a reduction in matriculation shares to the worse exam performance, instead of the better performance which could induce students to choose better universities.

@@

In Japan, for admission for most (almost all public) universities, students are required to take two exams.
The first-stage test is called Center Test.
Students take an exam on consecutive two days (Saturday and Sunday) on mid-January.
While different students can choose which subjects to take, most public universities require students to take exams on social science, language, and English on the first day and math and natural science on the second day.
The exams start at 9:30 AM on both days and end at 6:10 PM on the first day and 5:50 PM on the second day.
Questions are multiple-choice and common for all exam takers across Japan.
High-school seniors take the test at designated cites in the area where their high schools are located.
On the other hand, high-school graduates are assigned to test cites in the area where the homes used in their application forms are located.

Exam takers do not receive their scores until the next May at earliest.
However, they can record their answers on their exam booklets and can bring them back home.
Hence, they know their scores by comparing their own answers and correct answers, which are made public through newspapers or websites of cramming schools.
After taking Center Test, students apply for public and private universities.\footnote{
  There are private universities who accept applications before Center Test.
}
Applicants for public universities typically take the second-stage exam.
This exam is made by each university, and students physically go to the universities and take the exam.
Therefore, every applicant for a university takes the second-stage exam at the same location on the same days.

Most public universities, including UTokyo, have three periods for the second-stage exam:
usually, the first one is at the end of February, the second one is on the first week of March, and the third one is on the second week of March.
Students can apply for only one university at each exam period.
While different universities accept applications for different periods, most universities have only one (typically the first period) or two (typically the first and the third periods) periods.
Up to 2015, UTokyo had two exam periods, the first and the third ones, although most of the admissions were provided for exam takers at the first exam period.\footnote{
  In 2015, while 3,008 students got admitted though the first-period exam, only 100 students got admitted through the third-period exam.
  % https://www.u-tokyo.ac.jp/ja/about/overview/e08_01_h27.html
}
In 2016, UTokyo abolished the third-period exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test.
In the latter process, students take interviews on November before Center Test, and after taking Center Test, final admissions are determined based on the results both of interviews and scores at Center Test.\footnote{
  In 2020, among 3,083 admitted students, only 73 students got admitted through this process.
  % https://www.u-tokyo.ac.jp/ja/about/overview/e08_01.html
}

In admission for UTokyo, scores at Center Test are used for two purposes for the first-period exam takers.
First, the scores are used for eligibility to take the second-stage exam.
Thresholds varying across years and across majors are set, and if scores at Center Test are below the thresholds, students cannot take the second-stage exam.
Since the thresholds are announced after the application, exam takers do not know if their scores are above or below the thresholds.
Secondly, the scores at Center Test are taken into consideration for admission.
The final score of a students is calculated by the weighted sum of exam scores at the first- and the second-stage exams.\footnote{
  In 2020, for the first-period exam takers, the weights for Center Test and the second-stage exam are 20\% and 80\%.
  Also, until 2015, for the third-period exam takers, scores at Center Test were used only for eligibility and were not accounted for the final admission.
}

@@

I use two sets of data: weather and matriculation information for UTokyo.
For weather information, I get data from \Citeauthor{jma}.
Their website maintains the past weather across Japan.
In this study, based on hourly weather on exam days at prefecture capitals, I use average weathers between 6AM to 6PM.
Prefecture capitals tend to be most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located at prefecture capitals.
%\footnote{
%  According to inter-edu, \url{https://www.inter-edu.com/univ/2019/jisseki/todai/ranking/}
%}

For matriculation information for UTokyo, I use University Basic Information maintained by \Citeauthor{univ_info}.
This data contains information from 2012 to 2020 on the number of matriculated students for each university by prefectures at which their high schools are located.
I create the matriculation share of each prefecture, which is the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
  Ideally, the information on admission rather than matriculation should be used since matriculation depends on exam scores and decision to go to the university or not.
  Due to the lack of the number of admitted students by prefecture, I use the information on matriculation.
  For UTokyo, the number of admissions and the number of matriculations are very close:
  In 2020, among 3,083 admitted students, 3,064 students matriculate at UTokyo.
  Moreover, it is unlikely that weathers on exam days affect decisions of admitted students to matriculate or not.
}

The summary statistics are provided in Table \ref{tab:sum_stat}.
While the mean of the matriculation share (\%) is $2.08$,\footnote{
  Since there are matriculations from abroad, the mean value does not coincide with $1 / 47 \approx 2.12\%$.
  I do not consider matriculations from abroad in the analyses since their admission is mostly based on interviews and essays.
} the distribution is starkly skewed.
As shown in Figure \ref{fig:admission_map}, many prefecture have less 1\% shares.
Also, the matriculation shares of the top 5 prefectures total more than 60\%.
This results in a small median matriculation share, $0.79 \%$.

%\begin{table}[H]
%  \centering
%  \caption{Summary Statistics}
%  \resizebox{0.8\linewidth}{!}{
%  \input{"../Output/tex/sum_stat.tex"}
%  }
%  \label{tab:sum_stat}
%  \footnotesize
%  \begin{tablenotes}
%    \item 
%      Notes:
%      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
%      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
%  \end{tablenotes}
%\end{table}

@@

The objective of the analysis is to analyze the effect of temperature and other weather variables on exam days on the matriculation share for UTokyo.
The reason why I use the matriculation share for UTokyo is as follows:
consider an matriculation share for a middle-ranked university.
Suppose also that low temperature has a negative impact on exam scores.
Then, 
(i) students from the prefecture who would get into the middle-ranked university if the temperature was higher could go to a lower-ranked university, but
(ii) students from the prefecture who would get into a higher-ranked university may get into the middle-ranked university.
Hence, the matriculation share of the prefecture for the middle-ranked university may not be affected by low temperature.
However, the second effect is unlikely to be large for UTokyo for the following reasons.
First, UTokyo is known to be the best university in Japan.
Secondly, since UTokyo is a national university, the tuition is cheaper than most private universities.\footnote{
  According to \citet{mext}, in 2018, the annual tuition for national universities was 538,633 JPY ($\approx$ 4,900 USD), while the average annual tuition for private university was 904,146 ($\approx$ 8,200 USD).
  %https://www.mext.go.jp/a_menu/koutou/shinkou/07021403/1412031_00001.htm
}
Therefore, I can rule out the second possibility and attribute a reduction in matriculation shares to the worse exam performance.

In the analyses, the outcome variable, $Y_{jt}$ is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
Let $T_{jt}$ be average temperature on exam days in $j$ in year $t$.
I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
I include other weather variables such as rainfall, snowfall, and cumulated snow on exam days as a vector $X_{jt}$.
As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
Finally, the error term is represented as $\epsilon_{jt}$.

I run the following regression equation:
\begin{equation*}
  Y_{jt} = f(T_{jt}) + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
\end{equation*}
I exploit the variation of temperature on exam days, which I consider exogenous after controlling for prefecture-specific time-variant factors and time-varying aggregate shocks through prefecture and year fixed effects.
As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variations in temperature on exam days.\footnote{
  Similar figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
}

One potential problem in the analysis is that a student from a high school in a prefecture does not necessarily take Center Test in the same municipality.
This means that, for these students, the weather at the exam cites are measured with errors.
The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get in any university for the first year and retake Center Test next year in his home prefecture.
I consider that, conditional on prefecture fixed effects, the measurement error is likely to be uncorrelated with the error term.
Hence, this classical measurement error can make the estimates conservative.

%\begin{figure}[H]
%  \centering
%  \caption{Average temperature on two exam days in each prefecture each year}
%  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
%  \label{fig:temperature_diff}
%  \footnotesize
%  \begin{tablenotes}
%    \item Notes:
%      Temperature at prefecture capitals between 6AM and 6PM on days of Center Test is used.
%      Average across two test days in each year is shown in the figure.
%      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
%  \end{tablenotes}
%\end{figure}

@@

The main empirical results are provided in Table \ref{tab:main_reg}.
The standard errors are clustered at the prefecture level.
The column (1) shows the result with a linear specification.
While the point estimate is positive, which means matriculation shares are higher if an exam is held on warmer days, it is statistically insignificant. 
The estimates with a non-linear specification allowing for flexible temperature effects (column (2)) show a negative and statistically significant impacts of cold weather. 
Since the mean matriculation share is $2.08$\%, the coefficient on the lowest temperature bins means that reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest bin, the matriculation share decreases by 9\%.
Moreover, due to the stark skewness in the distribution of matriculation shares, the median matriculation share is $0.79$.
Therefore, the same temperature change decreases the matriculation share by 22\% of the median value.
Also, the plateau effect of temperature above 6 $^o$C could be the reason why the linear specification in the column (1) could not capture the non-linear effect of temperature and why the coefficient is statistically insignificant.
Although for a quite different temperature range, similar plateau effects are found in \citet{Park2020a}.

In column (3) and (4), I add other weather variables.
While temperature coefficients are barely affected, I find that rainfall and snowfall during exam time do not impact the matriculation shares.
On the other hand, the cumulated snow on the ground has a negative impact.
To capture the effect of existence of snow on the ground, column (5) allows a non-linear effect of cumulated snow.
This specification gives a result that, when there is snow on the ground cumulated more than 10cm ($\approx$ 3 feet) decreases the matriculation share by 0.13 percentage point.

In summary, I find a both statistically and economically significant impacts of weather on exam days.
In particular, the estimation results show that low temperature and snow cumulated on the ground have negative impact on the matriculation shares for UTokyo.
In the next two subsections, I investigate the mechanisms underlying the findings.

%\begin{table}[H]
%  \center
%  \caption{Regression: Matriculation share (\%) and weather on exam days}
%  \input{"../Output/tex/main_reg.tex"}
%  \label{tab:main_reg}
%  \small
%  \begin{tablenotes}
%    \item
%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
%      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
%      Standard errors are clustered at the prefecture level.
%  \end{tablenotes}
%\end{table}

@@

One possible interpretation is that the temperature on exam days capture the weathers before the exam, which can affect preparation for the exam. 
For instance, cold weather can make it hard for students to focus on studying, or snowfalls can prevent students from going to schools or cramming schools for studying.
To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
The results in Table \ref{tab:reg_pre10} show statistically insignificant estimates for all the variables.
Therefore, I consider that the findings in Table \ref{tab:main_reg} are due to the effect of weather variables on the exam days.

%\begin{table}[H]
%  \center
%  \caption{Regression: Matriculation share (\%) and weather in the morning vs. during exam}
%  \scriptsize
%  \input{"../Output/tex/reg_morning_exam.tex"}
%  \label{tab:reg_morning_exam}
%  \scriptsize
%  \begin{tablenotes}
%    \item
%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
%      For variables in the morning, I use average weather variables at prefecture capitals between 6AM to 9AM on exam days.
%      For variables during the exam, I use average weather variables at prefecture capitals between 9AM to 6PM on exam days.
%      Standard errors are clustered at the prefecture level.
%  \end{tablenotes}
%\end{table}

@@

In this paper I study the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
Instead of exam scores, I use the matriculation share for the most prestigious university in Japan, the University of Tokyo.
To identify the causal impact, I exploit the variation in weathers at each prefecture on exam days.
Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains largely unknown.
This study fills the gap and identifies the causal impact of winter weather on the matriculation.

The results show that both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam days.
Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage point, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
Moreover, having more than 10cm of snow on the ground decreases the share by 0.13 percentage point.
Using the weathers in the morning and during the exams, I find a suggestive evidence that the temperature effect is mainly caused by low temperature in the morning.
This result suggest that adverse conditions for exam takers on the way to test cites affect their cognitive performance.

Several implications can be derived from the findings.
First, the result that low temperature in the morning rather than during the exam matters suggest that equipments to improve the condition at the exam sites may have limited impacts.
Rather, investment on recovering students can result in better improvement.
For instance, providing socks and slippers for students whose shoes and socks get wet due to walking through stacked snow.
Also, it may be effective to provide sufficient time before the exam at the exam site so that students can recover in a warm room.
%This study provides guidance on how to set the leveling field for exam takers across Japan.

Secondly, my results have implications on the matriculation process of universities.
Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measure to select students.
Examples include extracurricular activities and statement of purposes, which are actively utilized in other countries such as the U.S..
On the other hand, it may be effective to change the weights for Center Test and the second-stage exam.
Since the second-stage exam is held at each university, all exam takers are exposed to similar environments.
This rules out the possibility that exam takers at different places are affected differently by their conditions.
Given the importance of exam results for later life outcomes, it is desirable that universities take measures to mitigate the effect of nuisance factors on matriculation.

@@

\begin{figure}[H]
  \centering
  \caption{Average temperature on two exam days in each prefecture each year}
  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
  \label{fig:temperature_diff}
  \footnotesize
  \begin{tablenotes}
    \item Notes:
      Temperature at prefecture capitals between 6AM and 6PM on days of Center Test is used.
      Average across two test days in each year is shown in the figure.
      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
  \end{tablenotes}
\end{figure}

@@

\begin{table}[H]
  \centering
  \caption{Summary Statistics}
  \resizebox{0.8\linewidth}{!}{
  \input{"../Output/tex/sum_stat.tex"}
  }
  \label{tab:sum_stat}
  \footnotesize
  \begin{tablenotes}
    \item 
      Notes:
      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
  \end{tablenotes}
\end{table}

\begin{table}[H]
  \center
  \caption{Regression: Matriculation share (\%) and weather on exam days}
  \input{"../Output/tex/main_reg.tex"}
  \label{tab:main_reg}
  \small
  \begin{tablenotes}
    \item
      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
      I use weather variables at prefecture capitals between 6AM and 6PM on days of Center Test.
      Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{table}

>>>>

This study analyzes the effect of winter weathers on exam outcomes in Japan.
Most public universities in Japan require high school seniors and graduates to take a centralized test, called National Center Test for University Admission (Center Test henceforth), for admission.
Students take the exam on the same dates in mid-January in their prefectures.
This creates a variation in weathers to which they are exposed on the exam dates.
I use the weather on the dates of Center Test and investigate its effect on the matriculation for the University of Tokyo (UTokyo henceforth).
The advantage of using the matriculation share for UTokyo as an outcome is that it is the most prestigious university in Japan.
This allows me to attribute a reduction in matriculation shares to the worse exam performance, instead of the better performance which could induce students to choose better universities.

@@

In Japan, for admission to most (almost all public) universities, students are required to take two exams.
The first-stage test is called Center Test.
Students take an exam on consecutive two days (Saturday and Sunday) in mid-January.
%While different students can choose which subjects to take, most public universities require students to take exams on social science, language, and English on the first day and math and natural science on the second day.
The exams start at 9:30 AM on both days and end at 6:10 PM on the first day and 5:50 PM on the second day.
Questions are multiple-choice and common for all exam takers across Japan.
High-school seniors take the test at designated sites in the area where their high schools are located.
On the other hand, high-school graduates are assigned to test sites in the area where the homes used in their applications are located.

On exam dates, heave snows can affect public transportation.
If this makes it difficult for exam takers to come to exam sites on time, the exam can start a few hours later than scheduled to accommodate them.
It is also possible that affected students take make-up exams a week later.

%Exam takers do not receive their scores until the next May at earliest.
%However, they can record their answers on their exam booklets and can bring them back home.
%Hence, they know their scores by comparing their own answers and correct answers, which are made public through newspapers or websites of cramming schools.
%After taking Center Test, students apply for public and private universities.\footnote{
%  There are private universities who accept applications before Center Test.
%}
%Applicants for public universities typically take the second-stage exam.

After Center Test, applicants for public universities typically take the second-stage exam.
This exam is made by each university, and students physically go to the universities and take the exam.
Therefore, every applicant for a university takes the second-stage exam at the same location on the same days.
UTokyo has the second-stage exam at the end of February for two days.\footnote{
  Up to 2015, UTokyo had another second-stage exam in March and a small number of exam takers got admitted through the exam (around 3\% of all admitted students).
%  Most of the admissions were provided for exam takers on February:
%  In 2015, among 3,108 admitted students, only 100 exam takers in March got admitted.
  In 2016, UTokyo abolished the March exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test (around 2\% of all admitted students).
  Since the majority of students are admitted through the second-stage exam on February, I focus on the admission process for those students. 
}

%Most public universities, including UTokyo, have three periods for the second-stage exam:
%usually, the first one is at the end of February, the second one is on the first week of March, and the third one is on the second week of March.
%Students can apply for only one university at each exam period.
%While different universities accept applications for different periods, most universities have only one (typically the first period) or two (typically the first and the third periods) periods.
%Up to 2015, UTokyo had two exam periods, the first and the third ones, although most of the admissions were provided for exam takers at the first exam period.\footnote{
%  In 2015, while 3,008 students got admitted through the first-period exam, only 100 students got admitted through the third-period exam.
%  % https://www.u-tokyo.ac.jp/ja/about/overview/e08_01_h27.html
%}
%In 2016, UTokyo abolished the third-period exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test.
%In the latter process, students take interviews in November before Center Test, and after taking Center Test, final admissions are determined based on the results both of interviews and scores at Center Test.\footnote{
%  In 2020, among 3,083 admitted students, only 73 students got admitted through this process.
%  % https://www.u-tokyo.ac.jp/ja/about/overview/e08_01.html
%}

In admission for UTokyo, scores at Center Test are used for two purposes.
First, the scores are used for eligibility to take the second-stage exam.
Thresholds varying across years and across majors are set, and if scores at Center Test are below the thresholds, students cannot take the second-stage exam.
Since the thresholds are announced after the application, exam takers do not know if their scores are above or below the thresholds.
Secondly, the scores at Center Test are taken into consideration for admission.
The final score of a student is calculated by the weighted sum of exam scores at the first- and second-stage exams.\footnote{
  In 2020, for the first-period exam takers, the weights for Center Test and the second-stage exam are 20\% and 80\%.
  %Also, until 2015, for the third-period exam takers, scores at Center Test were used only for eligibility and were not accounted for the final admission.
}

@@

I use two sets of data: weather and matriculation information for UTokyo.
For weather information, I get data from \Citeauthor{jma}.
Their website maintains the past weather across Japan.
In this study, based on hourly weather on exam days at prefecture capitals, I use average weathers between 6 AM to 6 PM.
Prefecture capitals tend to be most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located at prefecture capitals.
%\footnote{
%  According to inter-edu, \url{https://www.inter-edu.com/univ/2019/jisseki/todai/ranking/}
%}

For matriculation information for UTokyo, I use University Basic Information maintained by \Citeauthor{univ_info}.
This data contains information from 2012 to 2020 on the number of matriculated students for each university by prefectures at which their high schools are located.
I create the matriculation share of each prefecture, which is the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
  Ideally, the information on admission rather than matriculation should be used since matriculation depends on exam scores and the decision to go to the university or not.
  Due to the lack of the information on the number of admitted students by prefecture, I use the information on matriculation.
  For UTokyo, the number of admissions and the number of matriculations are very close:
  In 2020, among 3,083 admitted students, 3,064 students matriculate at UTokyo.
  Moreover, it is unlikely that weathers on exam days affect decisions of admitted students to matriculate or not.
}

The summary statistics are provided in Table \ref{tab:sum_stat}.
While the mean of the matriculation share (\%) is $2.08$,\footnote{
  Since there are matriculations from abroad, the mean value does not coincide with $1 / 47 \approx 2.12\%$.
  I do not consider matriculations from abroad in the analyses since their admission is mostly based on interviews and essays.
} the distribution is starkly skewed.
As shown in Figure \ref{fig:admission_map}, many prefectures have less than 1\% shares.
Also, the matriculation shares of the top 5 prefectures total more than 60\%.
This results in a small median matriculation share, $0.79 \%$.

%\begin{table}[H]
%  \centering
%  \caption{Summary Statistics}
%  \resizebox{0.8\linewidth}{!}{
%  \input{"../Output/tex/sum_stat.tex"}
%  }
%  \label{tab:sum_stat}
%  \footnotesize
%  \begin{tablenotes}
%    \item 
%      Notes:
%      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
%  \end{tablenotes}
%\end{table}

@@

The objective of the analysis is to analyze the effect of temperature and other weather variables on exam days on the matriculation share for UTokyo.
The reason why I use the matriculation share for UTokyo is as follows:
consider a matriculation share for a middle-ranked university.
Suppose also that low temperature has a negative impact on exam scores.
Then, 
(i) students from the prefecture who would get into the middle-ranked university if the temperature was higher could go to a lower-ranked university, but
(ii) students from the prefecture who would get into a higher-ranked university may get into the middle-ranked university.
Hence, the matriculation share of the prefecture for the middle-ranked university may not be affected by low temperature.
However, the second effect is unlikely to be large for UTokyo for the following reasons.
First, UTokyo is known to be the best university in Japan.\footnote{
  According to \citet{usnews}, UTokyo is the highest-ranked university in Japan (73rd ranked in the world ranking).
  The second highest-ranked university in Japan is Kyoto University, which is 125th ranked in the world ranking.
}
Secondly, since UTokyo is a national university, the tuition is cheaper than most private universities.\footnote{
  According to \citet{mext}, in 2018, the annual tuition for national universities was 538,633 JPY ($\approx$ 4,900 USD), while the average annual tuition for private university was 904,146 ($\approx$ 8,200 USD).
  %https://www.mext.go.jp/a_menu/koutou/shinkou/07021403/1412031_00001.htm
}
Therefore, I can rule out the second possibility and attribute a reduction in matriculation shares to the worse exam performance.

In the analyses, the outcome variable, $Y_{jt}$ is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
Let $T_{jt}$ be the average temperature on exam days in $j$ in year $t$.
I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
I include other weather variables such as rainfall, snowfall, and cumulated snow on exam days as a vector $X_{jt}$.
As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
Finally, the error term is represented as $\epsilon_{jt}$.

I run the following regression equation:
\begin{equation*}
  Y_{jt} = f(T_{jt}) + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
\end{equation*}
I exploit the variation of temperature on exam days, which I consider exogenous after controlling for prefecture-specific time-invariant factors and time-varying aggregate shocks through prefecture and year fixed effects.
As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variations in temperature on exam days.\footnote{
  Figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
}

One potential problem in the analysis is that a student from a high school in a prefecture does not necessarily take Center Test in the same municipality.
This means that, for these students, the weather at the exam sites is measured with errors.
The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get into any university for the first year and retake Center Test next year in his home prefecture.
I consider that, conditional on prefecture fixed effects, the measurement error is likely to be uncorrelated with the error term.
Hence, this classical measurement error can make the estimates conservative.

%\begin{figure}[H]
%  \centering
%  \caption{Average temperature on two exam days in each prefecture each year}
%  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
%  \label{fig:temperature_diff}
%  \footnotesize
%  \begin{tablenotes}
%    \item Notes:
%      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
%      Average across two test days in each year is shown in the figure.
%      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
%  \end{tablenotes}
%\end{figure}

@@

The main empirical results are provided in Table \ref{tab:main_reg}.
The standard errors are clustered at the prefecture level.
The column (1) shows the result with a linear specification.
While the point estimate is positive, which means matriculation shares are higher if an exam is held on warmer days, it is statistically insignificant. 
The estimates with a non-linear specification allowing for flexible temperature effects (column (2)) show a negative and statistically significant impact of cold weather. 
Since the mean matriculation share is $2.08$\%, the coefficient on the lowest temperature bins means that, by reducing the temperature from the reference bin (between 3 and 6 $^o$C) to the lowest bin, the matriculation share decreases by 9\%.
Moreover, due to the stark skewness in the distribution of matriculation shares, the median matriculation share is $0.79$.
Therefore, the same temperature change decreases the matriculation share by 22\% of the median value.
Also, the plateau effect of temperature above 6 $^o$C could be the reason why the linear specification in the column (1) could not capture the non-linear effect of temperature and why the coefficient is statistically insignificant.
Although for a quite different temperature range, similar plateau effects are found in \citet{Park2020a}.

In column (3) and (4), I add other weather variables.
While temperature coefficients are barely affected, I find that rainfall and snowfall during exam time do not impact the matriculation shares.
On the other hand, the cumulated snow on the ground has a negative impact.
To capture the effect of the existence of a certain amount of snow on the ground, column (5) allows a non-linear effect of cumulated snow.
This specification gives a result that, snow on the ground cumulated more than 10cm ($\approx$ 3 feet) decreases the matriculation share by 0.13 percentage point.

In summary, I find a both statistically and economically significant impacts of weather on exam days.
In particular, the estimation results show that low temperature and snow cumulated on the ground have negative impacts on the matriculation shares for UTokyo.
In the next two subsections, I investigate the mechanisms underlying the findings.

%\begin{table}[H]
%  \center
%  \caption{Regression: Matriculation share (\%) and weather on exam days}
%  \input{"../Output/tex/main_reg.tex"}
%  \label{tab:main_reg}
%  \small
%  \begin{tablenotes}
%    \item
%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
%      Standard errors are clustered at the prefecture level.
%  \end{tablenotes}
%\end{table}

@@

One possible interpretation is that the temperature on exam days captures the weather before the exam, which can affect preparation for the exam. 
For instance, cold weather can make it hard for students to focus on studying, or snowfalls can prevent students from going to schools or cramming schools for studying.
To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
The results in Table \ref{tab:reg_pre10} show statistically insignificant estimates for all the variables.
Therefore, I consider that the findings in Table \ref{tab:main_reg} are due to the effect of weather variables on the exam days.

%\begin{table}[H]
%  \center
%  \caption{Regression: Matriculation share (\%) and weather in the morning vs. during exam}
%  \scriptsize
%  \input{"../Output/tex/reg_morning_exam.tex"}
%  \label{tab:reg_morning_exam}
%  \scriptsize
%  \begin{tablenotes}
%    \item
%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
%      For variables in the morning, I use average weather variables at prefecture capitals between 6 AM to 9 AM on exam days.
%      For variables during the exam, I use average weather variables at prefecture capitals between 9 AM to  on exam days.
%      Standard errors are clustered at the prefecture level.
%  \end{tablenotes}
%\end{table}

@@

This paper studies the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
Instead of exam scores, I use the matriculation share for the most prestigious university in Japan, the University of Tokyo.
To identify the causal impact, I exploit the variation in weathers at each prefecture on exam days.
Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains largely unknown.
This study fills the gap and identifies the causal impact of winter weather on the matriculation.

The results show that both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam days.
Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage point, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
Moreover, having more than 10cm of snow on the ground decreases the share by 0.13 percentage point.
Using the weathers in the morning and during the exams, I find suggestive evidence that the temperature effect is mainly caused by low temperature in the morning.
This result suggests that adverse conditions for exam takers on the way to test sites affect their cognitive performance.

Several implications can be derived from the findings.
First, the result that low temperature in the morning rather than during the exam matters suggest that equipments to improve the condition at the exam sites may have limited impacts.
Rather, for instance, it may be effective to provide sufficient time before the exam at the exam site so that students can recover in a warm room.
%For instance, it can be effective socks and slippers for students whose shoes and socks get wet due to walking through stacked snow.
%This study provides guidance on how to set the leveling field for exam takers across Japan.

Secondly, my results have implications for the matriculation process of universities.
Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.
Examples include extracurricular activities and statement of purposes, which are actively utilized in other countries such as the U.S..
On the other hand, it may be effective to change the weights for Center Test and the second-stage exam.
Since the second-stage exam is held at each university, all exam takers are exposed to similar environments.
This rules out the possibility that exam takers at different places are affected differently by their conditions.
Given the importance of exam results for later life outcomes, it is desirable that universities take measures to mitigate the effect of nuisance factors on matriculation.

@@

\begin{figure}[H]
  \centering
  \caption{Average temperature on two exam days in each prefecture each year}
  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
  \label{fig:temperature_diff}
  \footnotesize
  \begin{tablenotes}
    \item Notes:
      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
      Average across two test days in each year is shown in the figure.
      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
  \end{tablenotes}
\end{figure}

@@

\begin{table}[H]
  \centering
  \caption{Summary Statistics}
  \resizebox{0.8\linewidth}{!}{
  \input{"../Output/tex/sum_stat.tex"}
  }
  \label{tab:sum_stat}
  \footnotesize
  \begin{tablenotes}
    \item 
      Notes:
      Matriculation share (\%) is the share of newly matriculated students to the University of Tokyo from each prefecture.
      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
  \end{tablenotes}
\end{table}

\begin{table}[H]
  \center
  \caption{Regression: Matriculation share (\%) and weather on exam days}
  \input{"../Output/tex/main_reg.tex"}
  \label{tab:main_reg}
  \small
  \begin{tablenotes}
    \item
      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
      Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{table}

\begin{table}[H]
  \center
  \caption{Regression: Matriculation share (\%) and weather in the morning vs. during exam}
  \scriptsize
  \input{"../Output/tex/reg_morning_exam.tex"}
  \label{tab:reg_morning_exam}
  \scriptsize
  \begin{tablenotes}
    \item
      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
      For variables in the morning, I use average weather variables at prefecture capitals between 6 AM to 9 AM on exam days.
      For variables during the exam, I use average weather variables at prefecture capitals between 9 AM to 6 PM on exam days.
      Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{table}
